Vulnerability Analysis of Container Images in Neuroimaging

### 2020-07-30 paper.tex
ubuntu database fixes

\affil[1]{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}
\maketitle

@@

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distributions, Anchore refers to
different sources. Table~\ref{database} displays Anchore's vulnerability sources for
Ubuntu, Debian, Alpine, and Centos, which are present inside taken images.
Anchore also refers to National
Vulnerability Database (NVD) to get metadata of vulnerabilities.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
connects to the running containers that needs to be scanned through SSH, and queries the package manager
in the container. We use Vuls 0.9.0, executed through Docker image
\texttt{vuls/vuls:0.9.0}. At the time of this study, Vuls gets vulnerability feed
from a configured set of sources. Table~\ref{database} lists vulnerability databases
referred by Vuls for scanned four OS distributions i.e. Alpine, Ubuntu, Debian, and Centos.
Apart from this, like Anchore, Vuls also refers NVD database for getting vulnerability metadata.
Table~\ref{database} shows that Vuls
refers to Open Vulnerability and Assessment Language (OVAL) database for Ubuntu, Debian, and Centos.
It is worth noting that there is
no vulnerability data for Ubuntu 17.04 and 17.10 distributions in OVAL database, meaning that images
with these distributions cannot be scanned with Vuls.

@@

Clair (\url{https://github.com/quay/clair}) is an open-source and extensible
vulnerability scanner for Docker and appc container images, developed by
CoreOS (now Container Linux), a Linux distribution to deploy container
clusters. Clair has a client-server architecture, in which the server
scans Docker images layer by layer and maintains a database of vulnerabilities. We use Clair through Clair-scanner
(\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
of container images against a local Clair server. Clair-scanner scans the image,
prepares a list of vulnerabilities, compares that list against a
whitelist, and flags vulnerabilities that are not present in the whitelist.
In our experiments, we did not use a whitelist to filter scanning results in
order to make a fair comparison between scanners.
Clair-scanner maintains a Docker image with the up-to-date vulnerability
database from a set of different sources. Table~\ref{database} lists
vulnerability databases that Clair referred for Alpine, Ubuntu, Debian, and Centos.
Clair also uses NVD database for getting vulnerability metadata.
We use Clair version 2.0.6, executed through
Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
database, we use Docker image \texttt{arminc/clair-db:latest}, last
updated on 2019-09-18.

@@

\subsection{Ubuntu Release types and its Vulnerability statuses}

BIDS apps and Boutiques images in our experiments have four Linux
distributions i.e. Ubuntu, CentOS, Debian, and Alpine. 
Out of these distributions, Ubuntu assigns a vulnerability status to
all vulnerabilities before keeping them in its vulnerability database.
Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
Ubuntu keeps a record of Ubuntu-specific vulnerabilities in Ubuntu CVE Tracker using their CVE
numbers. In this paper, we use vulnerability and CVE interchangeably.
The vulnerability status in Ubuntu CVE Tracker is subjected to change
depending on the work progress to fix that vulnerability.
%Regarding Ubuntu, it has different
%types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
%Ubuntu maintains its vulnerability data in Ubuntu CVE tracker, which is referred by Anchore and Clair.
%There is another vulnerability database i.e. Open Vulnerability and Assessment Language (OVAL) repository,
%which is maintained by MITRE corporation. Vuls refers to OVAL repository for getting Ubuntu vulnerability feed.
%The vulnerability data format of both databases is different. OVAL keeps a separate xml file for each release,
%which contains that release specific vulnerability information.
Ubuntu keeps a separate file for each vulnerability, which
has an entry for all Ubuntu releases combined with the current status
of that vulnerability in that release.
Further, in Ubuntu a particular release can be of different types i.e. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release. 
Through our experiments, we find that Anchore and Clair report Ubuntu vulnerabilities 
differently depending on either the different Ubuntu release type or vulnerability status. It is 
important to provide an overview of these Ubuntu releases types and vulnerability statuses, 
since Ubuntu is heavily utilized in our experiments. 
Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of ESM release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
exists in LTS.

As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
to LTS release only while collecting data from the vulnerability databases.
More interestingly, Clair refers to ESM release vulnerability database, however, this may lead to discrepancies in results.
Further, if an image is using a Linux release where EOL has been reached that image may
turns to be vulnerable as it is not possible to retrieve any updates.

In Ubuntu CVE Tracker, all Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a vulnerability status
(\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>) \\
\newline\\
For a given release, the vulnerability status can be any one of the following:

\textbf{DNE (Does Not Exist):} The package does not exist in the
		archive.

@@

\textbf{not-affected:} The package, while related to the
		CVE in some way, is not affected by the issue. The <notes> should
		provide detailed information, if needed. For instance, if the given
		status is "not-affected (1.14.6-1.1)" then this indicates that this specific
		package version is not affected.

\textbf{needed:} The package is vulnerable to the
		CVE and needs to be fixed.

\textbf{active:} The package is vulnerable to the
		CVE, needs fixing, and is actively being worked on.

\textbf{ignored:} The package, while related to the
		CVE in some way, is being ignored for some reason. The
		<notes> should provide that reason. For instance, if status looks like
		"ignored (reached end-of-life)", this means that the given Ubuntu release already reached
		end-of-life, so this CVE is ignored by Ubuntu. However, if there
		is extended security support for this release then this
		CVE will be handled in ESM release.

\textbf{pending:} The package is vulnerable and
                  has been fixed but an update has not been yet uploaded or
		  published. The <version> is given to indicate the particular 
		  version where the fix has been done.

\textbf{deferred:} The package is vulnerable, but 
                   its fix has been deferred for some reason. The <notes>
		   should provide further details. If a date is mentioned, e.g.
		   "deferred (2015-02-02)", the given date specifies the date when
		   the CVE was deferred.

\textbf{released:} The package was vulnerable, but
		an update has been already uploaded and published, e.g. "released (1.2.3)",
		<version> indicates the first version where the fix was applied.

\textbf{released-esm:} The package was vulnerable and
		an update has been already uploaded and published. However,
		this update is published in the Ubuntu ESM release only and not in LTS.
		The fixed version of such packages is appended by either
		+esm or \char`\~esm, indicating that this package version is available
		only via ESM.

Figure~\ref{example} illustrates how the information of a CVE is represented
in the Ubuntu CVE Tracker.

\begin{figure}[!ht]
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a CVE in Ubuntu CVE Tracker}
\end{figure}
\vspace*{-7mm}
\section{Reducing the amount of vulnerabilities}

@@

Table~\ref{table1} shows the number of vulnerabilities in the different images,
detected by each of the scanners. Image labels from a to al represents
Docker images, whereas remaining ones belong to Singularity.
Vuls shows \textit{no data} for images \texttt{bids/antscorticalthickness:v2.2.0-1} and \texttt{bids/afni\_proc:latest},
which have Ubuntu 17.04 and 17.10 OS distribution respectively. This is because there is no
vulnerability data present in OVAL database, which Vuls refers for Ubuntu distributions, for these two releases.

Figure~\ref{fig:graph1} provides more image-specific information.
It represents the number of vulnerabilities that are present inside each images.
The overall trend shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
This Figure also infers that the Alpine distribution, being a
lightweight distribution, has the least number of vulnerabilities, whereas more vulnerabilities are reported for
distributions with more packages such as Ubuntu.
We also analyze that out of the total Docker images scanned by our experiments, Debian reports more high-level vulnerabilties, as
classified by databases, than others.
\begin{table*}
\csvreader[%
 tabular={|c|c|c|c|c|c|},
	table head = \hline\textbf{Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
	late after line= \\,
        late after last line=\\\hline %
	]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
        {\labels & \names & \A & \C & \V & \Stools}
       \centering
	\vspace*{1mm}
	\caption{\label{table1}Number of vulnerabilities by scanners (all Centos images are highlighted)} 
\end{table*}

@@

Our experiments concluded considerable discrepancies in the results obtained by
these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
While comparing scanner results, we exluded all Centos images (highlighted images in Table~\ref{table1})
and two other images \texttt{bids/antscorticalthickness:v2.2.0-1} and
\texttt{bids/antscorticalthickness:v2.2.0-1}. The reason behind excluding Centos images is that scanners report results using different
vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
to report pending patches that need to be applied to specific packages,
whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
vulnerabilities in packages. We exluded other two images because Vuls
can not scan these image, hence no results are present to compare.
In most cases,
Anchore reports more vulnerabilities than Vuls and Clair resulting in 
the Jaccard coefficient of 0.59 with both,
whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.83.
Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
the scanners in Docker images and the overlap between them.
This Figure also excludes Centos Docker images and other two non-comparable images.
It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 by Clair, and 325 by Vuls.

As the number and type of vulnerabilities reported by the these scanners are significantly different from each other,
we desire to investigate the reasons behind these differences.
Following our investigation, we are able to explain some of the reasons behind
the differences. 
Such reasons were resulted from the way these scanners function or behave 
in particular, the following actions by the scanners are indicative:
\begin{itemize}
   \item scanners ignoring vulnerabilities in Linux-kernel-header packages,
   \item scanners referring to different vulnerability databases,
   \item different frequency of updating their databases,
   \item bugs in scanners. 
\end{itemize}

@@

\textbf{Ubuntu CVEs with status as “Not-affected”:} Vuls reports vulnerabilities that have status
as "not-affected" in the Ubuntu database. It means that according to Ubuntu the image is not affected
by the particular vulnerability. In other words, Vuls reports vulnerabilities that it should not have been reported.
For example, when we scan an image having the Trusty release in it and Vuls reports CVE-2015-2305
in the package Cups. However, upon checking the Ubuntu vulnerability database, we find that package Cups in Trusty is not
affected by this CVE.

\textbf{Ubuntu CVEs with status as "Ignored (reached end-of-life)":}
Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
However, in Ubuntu 14.04 ESM release, these vulnerabilities may or may not be present.
Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
prior to the end-of-life. Only if it was vulnerable, Anchore reports it, otherwise it does not.
If this kind of vulnerability is present in ESM release then Clair reports it because it
only refers to ESM release. On the other hand, if the vulnerability
status in ESM release is "DNE" (Does Not Exist), then Clair does not report it. 
For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to its end-of-life.
Consequently, it is not reported by Anchore. This vulnerability has status as "DNE" in Trusty ESM
release so Clair also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
Clair's referring to Ubuntu 14.04 ESM release vulnerability database is incorrect.

@@

\textbf{Ubuntu CVEs with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair. 
		For instance, CVE-2019-13565, which is present in Ubuntu 14.04 LTS, is an example of such vulnerabilities. 
		We reported this bug as well to the Anchore development team through their Slack
		channel.

>>>>

\affil[1]{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}

\maketitle

@@

Anchore compares package versions, which are present inside the
image, with the vulnerability database in order to flag vulnerabilities.
To get a vulnerability feed of various OS distributions, Anchore refers to
different sources. Figure~\ref{database} displays Anchore's vulnerability sources for
Ubuntu, Debian, Alpine, and Centos, which are present inside taken images.
Anchore also refers to National
Vulnerability Database (NVD) to get metadata of vulnerabilities.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
offers both static and dynamic scanning, and both local and remote
scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
connects to the running containers that needs to be scanned through SSH, and queries the package manager
in the container. We use Vuls 0.9.0, executed through Docker image
\texttt{vuls/vuls:0.9.0}. At the time of this study, Vuls gets vulnerability feed
from a configured set of sources. Figure~\ref{database} lists vulnerability databases
referred by Vuls for scanned four OS distributions i.e. Alpine, Ubuntu, Debian, and Centos.
Apart from this, like Anchore, Vuls also refers NVD database for getting vulnerability metadata.
Figure~\ref{database} shows that Vuls
refers to Open Vulnerability and Assessment Language (OVAL) database for Ubuntu, Debian, and Centos.
It is worth noting that there is
no vulnerability data for Ubuntu 17.04 and 17.10 distributions in OVAL database, meaning that images
with these distributions cannot be scanned with Vuls.

@@

Clair (\url{https://github.com/quay/clair}) is an open-source and extensible
vulnerability scanner for Docker and appc container images, developed by
CoreOS (now Container Linux), a Linux distribution to deploy container
clusters. Clair has a client-server architecture, in which the server
scans Docker images layer by layer and maintains a database of vulnerabilities. We use Clair through Clair-scanner
(\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
of container images against a local Clair server. Clair-scanner scans the image,
prepares a list of vulnerabilities, compares that list against a
whitelist, and flags vulnerabilities that are not present in the whitelist.
In our experiments, we did not use a whitelist to filter scanning results in
order to make a fair comparison between scanners.
Clair-scanner maintains a Docker image with the up-to-date vulnerability
database from a set of different sources. Figure~\ref{database} lists
vulnerability databases that Clair referred for Alpine, Ubuntu, Debian, and Centos.
Clair also uses NVD database for getting vulnerability metadata.
We use Clair version 2.0.6, executed through
Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
database, we use Docker image \texttt{arminc/clair-db:latest}, last
updated on 2019-09-18.

@@

\subsection{Ubuntu Vulnerability Database}

\change{There are two types of vulnerability databases that are referred
by the scanners in these experiments. First one is Open Vulnerability and Assessment Language (OVAL)
database, which is an international open standard and a common means of determining the existence of
vulnerabilities in softwares. OVAL supports various OS distributions e.g. Ubuntu, Debian, Centos, etc.
Second type of databases used by scanners are vulnerability databases from specific OS vendors e.g. Alpine-SecDB
from Alpine,
Debian Bug Tracker from Debian, Ubuntu CVE Tracker from Ubuntu, etc., where they
keep a track of their OS-specific vulnerabilities by assigning a status.
%In particular, there is a discrepancy in the way Anchore and Clair
%interpret Ubuntu CVE Tracker.
Out of four distributions that are present in our images Vuls uses
OVAL database for Debian, Ubuntu, Centos and refers to Alpine-SecDB
database for Alpine as this distribution is currently not supported by OVAL.
Clair and Anchore mostly refers to vulnerability databases provided by specific OS
vendors except in one case, where Anchore refers to OVAL i.e. Centos.

The major discrepancies are shown by Anchore and Clair in Ubuntu. Both refers to Ubuntu CVE Tracker database for Ubuntu images.
The way in which both scanners interpret this database is different.
%
%There are different vulnerability databases, which have
%different formats of data.
%Out of which Open Vulnerability and Assessment Language (OVAL) is an international
%open standard and a common
%means of promoting publicly available security issues. 
%It provides details about software vulnerabilities. It helps to determine
%whether vulnerabilities exist in local machines or not. Apart from OVAL, operating system
%vendors also keep track of their vulnerabilities separately and assign
%a status to each vulnerability.
%For example, Ubuntu maintains
%Ubuntu CVE Tracker, Debian maintains Debian Security Bug Tracker, etc.
%Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
%by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
%In this paper, we use vulnerability and CVE interchangeably.
%Ubuntu CVE Tracker is used by Anchore and Clair in our experiments
%and there is discrepancies in the way both scanners interpret results.
%
%BIDS apps and Boutiques images in our experiments have four Linux
%distributions i.e. Ubuntu, CentOS, Debian, and Alpine. 
%Out of these distributions, Ubuntu assigns a vulnerability status to
%all vulnerabilities before keeping them in its vulnerability database.
%Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
%by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
%Ubuntu keeps a record of Ubuntu-specific vulnerabilities in Ubuntu CVE Tracker using their CVE
%numbers. In this paper, we use vulnerability and CVE interchangeably.
%The vulnerability status in Ubuntu CVE Tracker is subjected to change
%depending on the work progress to fix that vulnerability.
%
%Regarding Ubuntu, it has different
%types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
%Ubuntu maintains its vulnerability data in Ubuntu CVE tracker, which is referred by Anchore and Clair.
%There is another vulnerability database i.e. Open Vulnerability and Assessment Language (OVAL) repository,
%which is maintained by MITRE corporation. Vuls refers to OVAL repository for getting Ubuntu vulnerability feed.
%The vulnerability data format of both databases is different. OVAL keeps a separate xml file for each release,
%which contains that release specific vulnerability information.
Ubuntu CVE Tracker keeps a separate file for each vulnerability, which
has an entry for all Ubuntu releases combined with the current status
of that vulnerability in that release.
In particular, Clair and Anchore show discrepancies for Ubuntu 14.04 which have
two entries for each vulnerability, one for Ubuntu 14.04 Long Term Support (LTS)
and second for Ubuntu 14.04 Extended Security Maintenance (ESM) release. As Ubuntu 14.04 LTS
reached end-of-life on 2019-04-30, so Ubuntu ignores new vulnerabilities in LTS release and
fix them only in ESM release. Consequently, a same vulnerability may have different vulnerability status in LTS and ESM releases,
which is causing discrepancies. This is because Anchore refers to Ubuntu 14.04 LTS, whereas Clair refers to
ESM.
%Further, in Ubuntu a particular release can be of different types i.e. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release. 
%Through our experiments, we find that Anchore and Clair report Ubuntu vulnerabilities 
%differently depending on either the different Ubuntu release type or vulnerability status. 
It is important to provide an overview of these Ubuntu vulnerability statuses, 
since Ubuntu is heavily utilized in our experiments. 
%Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
%reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
%in the form of ESM release.
%ESM is a paid service that can be requested from Ubuntu to get security 
%updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
%databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
%exists in LTS.
%
%As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
%17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
%To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
%The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
%to LTS release only while collecting data from the vulnerability databases.
%More interestingly, Clair refers to ESM release vulnerability database, however, this may lead to discrepancies in results.
%Further, if an image is using a Linux release where EOL has been reached that image may
%turns to be vulnerable as it is not possible to retrieve any updates.
%
In Ubuntu CVE Tracker, for a vulnerability all Ubuntu releases are listed with the package name
in which that vulnerability exists and are entitled a vulnerability status
(\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\
\noindent <release>\_<source-package>: <status> (<version/notes>)
\newline\\
The <version/notes> given with a vulnerability status provide more
information about the vulnerability.
For a given release, the vulnerability status can be any one of the following:

\textbf{DNE (Does Not Exist):} The package does not exist in the
		release.

@@

\textbf{not-affected:} The package, while related to the
		vulnerability in some way, is not affected by the issue.
	%	The <notes> should
	%	provide detailed information, if needed.
		%For instance, if the given
		%status is "not-affected (1.14.6-1.1)" then this indicates that this specific
		%package version is not affected.

\textbf{needed:} The package is vulnerable and needs to be fixed.

\textbf{active:} The package is vulnerable, needs fixing, and is 
                 actively being worked on.

\textbf{ignored:} The package, while related to the
		vulnerability in some way, is being ignored for some reason. 
	%	The
	%	<notes> should provide that reason.
	%	For instance, if status looks like
	%	"ignored (reached end-of-life)", this means that the given Ubuntu release already reached
	%	end-of-life, so this CVE is ignored by Ubuntu. However, if there
	%	is extended security support for this release then this
	%	CVE will be handled in ESM release.

\textbf{pending:} The package is vulnerable and
                  has been fixed but an update has not been yet uploaded or
		  published.
		 % The <version> is given to indicate the particular 
		 % version where the fix has been done.

\textbf{deferred:} The package is vulnerable, but 
                   its fix has been deferred for some reason. 
		  % The <notes>
		  % should provide further details.
		  % If a date is mentioned, e.g.
		  % "deferred (2015-02-02)", the given date specifies the date when
		  % the CVE was deferred.

\textbf{released:} The package was vulnerable, but
		an update has been already uploaded and published.
	%	e.g. "released (1.2.3)",
	%	<version> indicates the first version where the fix was applied.

\textbf{released-esm:} The package was vulnerable and
		an update has been already uploaded and published. However,
		this update is published in the Ubuntu ESM release only and not in LTS.}
		%The fixed version of such packages is appended by either
		%+esm or \char`\~esm, indicating that this package version is available
		%only via ESM.
\newlne\\
Figure~\ref{example} illustrates how the information of a vulnerability is represented
in the Ubuntu CVE Tracker.

\begin{figure}[!ht]
	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
	{Figures/vulnExample2.png}}}
        \caption{\label{example} Representation of a vulnerability in Ubuntu CVE Tracker}
\end{figure}
\vspace*{-7mm}
\section{Reducing the amount of vulnerabilities}

@@

\change{Table~\ref{table1} shows the number of vulnerabilities in the different images,
detected by each of the scanners. Image labels from a to al represents
Docker images, whereas remaining ones belong to Singularity.
Vuls shows \textit{no data} for images \texttt{bids/antscorticalthickness:v2.2.0-1} and \texttt{bids/afni\_proc:latest},
which have Ubuntu 17.04 and 17.10 OS distribution respectively. This is because Vuls
cannot support scanning of these two distributions as they reached end of life.
For Centos images, Anchore and Clair gives scanning results using Red Hat Security Advisory
(RHSA) identifiers for Centos images, whereas Vuls uses CVE identifiers.
RHSA identifiers specifies security patches that are pending to apply and
CVE identifiers specifies vulnerabilities that exist in the system.
So, we mapped RHSA identifiers to corresponding CVE identifiers to make
a fair comparison of scanners. Table~\ref{table1} shows
all vulnerabilities using CVE identifiers.}
\newline\\
Figure~\ref{fig:graph1} provides more image-specific information.
It represents the number of vulnerabilities that are present inside each images.
The overall trend shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
This Figure also infers that the Alpine distribution, being a
lightweight distribution, has the least number of vulnerabilities, whereas more vulnerabilities are reported for
distributions with more packages such as Ubuntu.
We also analyze that out of the total Docker images scanned by our experiments, Debian reports more high-level vulnerabilties, as
classified by databases, than others.
\begin{table*}
\csvreader[%
 tabular={|c|c|c|c|c|c|},
	table head = \hline\textbf{Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
	late after line= \\,
        late after last line=\\\hline %
	]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
        {\labels & \names & \A & \C & \V & \Stools}
       \centering
	\vspace*{1mm}
	\caption{\label{table1}Number of vulnerabilities by scanners} 
\end{table*}

@@

\change{Our experiments concluded considerable discrepancies in the results obtained by
these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
While comparing scanner results, we exluded two images \texttt{bids/antscorticalthickness:v2.2.0-1} and
\texttt{bids/antscorticalthickness:v2.2.0-1} because Vuls
cannot scan these image, hence no results are present to compare.
%The reason behind excluding
%vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
%to report pending patches that need to be applied to specific packages,
%whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
%vulnerabilities in packages. We exluded other two images because Vuls
%can not scan these image, hence no results are present to compare.
In most cases,
Anchore reports more vulnerabilities than Vuls and Clair resulting in 
the Jaccard coefficient of 0.63 with Clair, 0.59 with Vuls,
whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.86.
Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
the scanners in Docker images and the overlap between them.
This Figure also excludes two non-comparable images, which cannot be scanned with Vuls.
It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 699 by Clair, and 536 by Vuls.}
\newline\\
As the number and type of vulnerabilities reported by the these scanners are significantly different from each other,
we desire to investigate the reasons behind these differences.
Following our investigation, we are able to explain some of the reasons behind
the differences. 
Such reasons were resulted from the way these scanners function or behave 
in particular, the following actions by the scanners are indicative:
\begin{itemize}
   \item scanners ignoring vulnerabilities in Linux-kernel-header packages,
   \item scanners referring to different vulnerability databases,
   \item different frequency of updating their databases,
   \item bugs in scanners. 
\end{itemize}

@@

\textbf{Ubuntu vulnerabilities with status as “Not-affected”:} Vuls reports vulnerabilities that have status
as "not-affected" in the Ubuntu database. It means that according to Ubuntu the image is not affected
by the particular vulnerability. In other words, Vuls reports vulnerabilities that it should not have been reported.
For example, when we scan an image having the Trusty release in it and Vuls reports CVE-2015-2305
in the package Cups. However, upon checking the Ubuntu vulnerability database, we find that package Cups in Trusty is not
affected by this vulnerability.

\textbf{Ubuntu vulnerabilities with status as "Ignored (reached end-of-life)":}
Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
However, in Ubuntu 14.04 ESM release, these vulnerabilities may or may not be present.
Anchore checks the last status of these vulnerabilities in LTS whether the package was vulnerable
prior to the end-of-life. Only if it was vulnerable, Anchore reports it, otherwise it does not.
If this kind of vulnerability is present in ESM release then Clair reports it because it
only refers to ESM release. On the other hand, if the vulnerability
status in ESM release is "DNE" (Does Not Exist), then Clair does not report it. 
For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to its end-of-life.
Consequently, it is not reported by Anchore. This vulnerability has status as "DNE" in Trusty ESM
release so Clair also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
Clair's referring to Ubuntu 14.04 ESM release vulnerability database is incorrect.

@@

\textbf{Ubuntu vulnerabilities with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair. 
		For instance, CVE-2019-13565, which is present in Ubuntu 14.04 LTS, is an example of such vulnerabilities. 
		We reported this bug as well to the Anchore development team through their Slack
		channel.
